Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-05-22 articles/formalism/sections/kernel_paintbrush.tex
Added some reference and some detail to kernel paintbrush section.
Cleaned up discussion of parity of filament and added discussion of Planck stacking.

The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.  The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted as a segment with $E>0$.  Since the overdensity will also have emission in total intensity, this naturally predicts a positive $T/E$ correlation for magnetized filaments.  The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.

The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.  This results in a non-zero $B$ pattern for the filament.  For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East.  \revisit{The non-zero $B$ result is somewhat surprising given that the polarization pattern is invariant under parity.}

Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
The description is also intuitive if we distort the shape of the filament.  If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.

The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and more so for a tighter radius of curvature.

>>>>

The kernel can be thought of as the orientable nib of a calligraphy pen or paintbrush that we can trace along the filament.  The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted as a segment with $E>0$.  Since the overdensity will also have emission in total intensity, this naturally predicts a positive $TE$ correlation for magnetized filaments.  The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.

The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.  This results in a non-zero $B$ pattern for the filament.  For a North--South filament, the $B$-mode pattern is positive on the North-East and South-West, and negative in the North-West and South-East.

The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.  However, unlike a complete ring, this filament is not a configuration with a definite parity.  Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.  A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.  A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.  We predict that it should be there in higher fidelity data.

The intuition from the real-space kernels holds also when we distort the shape of the filament.  If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.  The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.  The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
